---
title: "Simple Function-on-Scalar Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Multi-Level Data Function-on-Function Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Case: Modeling sagittal knee kinematics as a function of sagittal hip kinematics during walking

In this short example we will demonstrate how `FunInf` can be used to perform inference on a **function-on-function** regression model where there is hierarchical data. We will use the `Gait120_walk` data set where there are multiple strides included for each participant.

### Step 1: Load Data

```{r data, message=FALSE, warning=FALSE, out.width='70%', }
library(FunInf)
library(tidyverse)
library(viridis)

data("Gait120_walk")

n = nrow(data)
j = length(levels(data$Subject))
colours = data.frame("colours" = sample(turbo(1000), j), "Subject" = levels(data$Subject))
colours = left_join(data, colours, by = "Subject")

par(mfrow = c(1,2))
matplot(t(data$Hip), 
        main = "Hip Flexion", xlab = "% Gait Cycle", ylab = "Degrees",
        type = 'l', col = colours$colours)
matplot(t(data$Knee), 
        main = "Knee Flexion", xlab = "% Gait Cycle", ylab = "Degrees",
        type = 'l', col = colours$colours)

```

### Step 2: Estimate model with `refund::pffr`

```{r model, message=FALSE, warning=FALSE}
library(refund)


mod = pffr(formula = Knee ~ Hip,
           data = data, 
           bs.int = list(k = 10, m = c(2,1), bs = 'ps'), 
           bs.yindex = list(k = 10, m = c(2,1), bs = 'ps'),
           algorithm = 'bam')

```
### Step 3: Create list of bootstrap samples with `level.boot.list`

```{r bootlist}
set.seed(2026)

boot.list = level.boot.list(df = data, id = "Subject", B = 500)

```


### Step 4: Refit the model on the bootstrap samples with `fit.boots`

```{r bootco, warning=FALSE}

library(future)
library(future.apply)

boot.coefs = fit.boots(model = mod, boot.list = boot.list, ncores = 5)

```

### Step 5: Estimate correlation and multiplicity adjusted confidence bands with `estimate.cma`

```{r cma, warning=FALSE}

cma = lapply(boot.coefs, function(X){
  
    estimate.CMA(boot.grid = X$boots, est = X$original$value, alpha = 0.05)
  
})

```


### Step 6: Plot the coefficient function for Age
```{r plot, out.width='70%'}
ggplot(cma$`Hip(yindex)`, aes(x = ind, y = est, ymin = LCI, ymax = UCI))+
  geom_line()+
  geom_ribbon(alpha = 0.4, fill = "red")+
  geom_hline(yintercept = 0, lty = 2)+
  theme_light()+
  labs(x = "% Gait Cycle", y = "Beta")
```

Based on this we would say there is a consistent and significant positive association between hip flexion and knee flexion across the whole gait cycle.
