---
title: "Simple Function-on-Scalar Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple Function-on-Scalar Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Case: Modeling variability of the sagittal knee kineamtics during walking

In this short example we will demonstrate how `FunInf` can be used to perform inference on a **function-on-scalar** regression model where there is non-hierarchical data. We will use a summarized version of the `Gait120_walk` data set where the point-wise standard deviation of each subjects walking trials is the response variable and the subject age is our predictor.

### Step 1: Load and Summarize Data

```{r data, message=FALSE, warning=FALSE, out.width='70%', }
library(FunInf)
library(tidyverse)

data("Gait120_walk")

sum.data = data %>% group_by(Subject) %>% summarise(Age = Age[1])

n = nrow(sum.data)

KneeVar = matrix(NA, nrow = n, ncol = ncol(data$Knee))

for(i in 1:n){
  subj.data = filter(data, Subject == Subject[i])
  KneeVar[i,] = apply(subj.data$Knee, 2, sd)
  
}

sum.data$KneeVar = KneeVar

matplot(t(KneeVar), 
        main = "Knee Flexion", xlab = "% Gait Cycle", ylab = "Standard Deviation",
        type = 'l')

```

### Step 2: Estimate model with `refund::pffr`

```{r model, message=FALSE}
library(refund)

mod = pffr(formula = KneeVar ~ Age,
           data = sum.data, 
           bs.int = list(k = 20, m = c(2,1), bs = 'ps'), 
           bs.yindex = list(k = 20, m = c(2,1), bs = 'ps'))

```
### Step 3: Create list of bootstrap samples with `simple.boot.list`

```{r bootlist}
set.seed(2026)

boot.list = simple.boot.list(df = sum.data, B = 500)

```


### Step 4: Refit the model on the bootstrap samples with `fit.boots`

```{r bootco, warning=FALSE}

library(future)
library(future.apply)

boot.coefs = fit.boots(model = mod, boot.list = boot.list, ncores = 5)

```

### Step 5: Estimate correlation and multiplicity adjusted confidence bands with `estimate.cma`

```{r cma, warning=FALSE}

cma = lapply(boot.coefs, function(X){
  
    estimate.CMA(boot.grid = X$boots, est = X$original$value, alpha = 0.05)
  
})

```


### Step 6: Plot the coefficient function for Age
```{r plot, out.width='70%'}
ggplot(cma$`Age(yindex)`, aes(x = ind, y = est, ymin = LCI, ymax = UCI))+
  geom_line()+
  geom_ribbon(alpha = 0.4, fill = "red")+
  geom_hline(yintercept = 0, lty = 2)+
  theme_light()+
  labs(x = "% Gait Cycle", y = "Beta")
```

Based on this we would say that there is a small but significant decrease in knee flexion variability during walking with age between $~25-80\%$ of the gait cycle. In this case this corresponds roughly to mid-stance through to late swing.  
